Open-source landscape for 3D CSEM modelling

### 2020-04-09 manuscript/Manuscript.tex
Cleaning up code-section

% Remove once done
\newcommand{\itodo}[1]{\todo[color=blue!40!white, inline]{\sffamily #1}}
\newcommand{\mtodo}[1]{\todo[inline]{\sffamily #1}}
\newcommand{\etodo}[1]{\todo[color=blue!40!white]{#1}}
\newcommand{\dul}[1]{\underline{\underline{#1}}}
\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\rmk}[1]{{\color{red}{#1}}}

@@

\itodo{
We will have to decide on a Journal. Current suggestions:\\
- GMD: Geoscientific Model Development\\
- SIG: Surveys in Geophysics\\
- SE: Solid Earth\\
- GJI: Geophysical Journal International\\
- GP: Geophysical Prospecting\\
- GEO: Geophysics\\
- CAG: Computers and Geosciences\\
I think \emph{Geoscientific Model Development} and \emph{Surveys in Geophysics}
are the favoured currently. I personally would be very interested in GMD. What
do you think? Also interesting would be the GJI, because the MT comparison was
published there, so it would be in the same place.
}

@@

A second topic we want to address is verification. New codes are generally
verified against analytical solutions. However, analytical and semi-analytical
solutions only exist for very simple models. There is no possibility to check
how good a computed response is, expect for comparing the result from different
modellers. If different modellers using different discretisation and
implementations of Maxwell's equations yield the same result it can give
confidence in the accuracy.

@@

\section{Codes}

Intro to it; numerical approximations (FE, FD), differences in solvers,
gridding/meshing, boundary conditions, etc.

It is beyond the scope of this paper to go into every detail of the different
modellers, however, a quick blabla...

All the codes presented here
\begin{itemize}
  \item are \emph{just available} (you don't have to write someone and ask if
    you could have the code);
  \item are \emph{easy installable} (through \texttt{pip} or \texttt{conda});
  \item are under \emph{version control} and online either on GitHub or on
    GitLab, which includes possibilities of easy involvement by either creating
    an issue, reporting a bug, or filing a pull request; and
  \item are well documented and come with a lot of examples.
\end{itemize}

\begin{itemize}
  \item Code (license): \emg3d (Apache-2.0), custEM (LPGL-3.0), PETGEM
    (GPL-3.0), and \simpeg (MIT).
  \item Hosting: GitHub (\emg3d, \petgem, \simpeg); GitLab (\custem)
\end{itemize}

Each code should outline:

\begin{itemize}
  \item Equation system it solves;
  \item the used discretization possibilities;
  \item domains (frequency, time);
  \item details (anisotropy; el. perm. and mag. perm.);
  \item other things (inversion; other methods);
  \item speed and memory estimation;
  \item plans for next features.
  \item Inversion capabilities
  \item Time/frequency
  \item transmitter types
\end{itemize}

Basically summarize each code in three points:
\begin{itemize}
  \item Brief intro and main features
  \item Main selling point
  \item Planned features
\end{itemize}

Cite for all: NumPy, SciPy.

The codes under consideration are presented here in alphabetical order.

@@

\cite{GEO.19.Rochlitz}

FEniCS \citep{CSE.15.Alnaes}

@@

\cite{GJI.19.CastilloReyes}

FEniCS \citep{CSE.15.Alnaes}

@@

\cite{CAG.15.Cockett}

PARDISO \citep{FGCS.04.Schenk}

\section{Comparison}

@@

\section{Discussion}

@@

\section{Conclusions}

@@

\section{Acknowledgment}

\itodo{Write here your fundings; and potentially also minor contributors etc.}

@@

\section{Data}

@@

% REFERENCES

\bibliographystyle{Refs}          % Modified SEG bibliography style.
\bibliography{Refs}

>>>>

% Remove once done
\newcommand{\mycom}[2][]{
  \todo[]{\textbf{\uppercase{[#1]}}:~#2}}
\newcommand{\imycom}[2][]{
  \todo[inline]{\textbf{\uppercase{[#1]}}:~#2}}
\newcommand{\dul}[1]{\underline{\underline{#1}}}
\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\rmk}[1]{{\color{red}{#1}}}

@@

\imycom[DW]{
  For comments in the margin, use:\\[.2cm]
  \qquad\texttt{\textbackslash mycom[YOURINITIALS]\{comment\}}\\[.2cm]
  and for inline comments, use:\\[.2cm]
  \qquad\texttt{\textbackslash imycom[YOURINITIALS]\{comment\}}
}

\imycom[DW]{
We will have to decide on a Journal. Current suggestions:\\
- GMD: Geoscientific Model Development\\
- SIG: Surveys in Geophysics\\
- SE: Solid Earth\\
- GJI: Geophysical Journal International\\
- GP: Geophysical Prospecting\\
- GEO: Geophysics\\
- CAG: Computers and Geosciences\\
I think \emph{Geoscientific Model Development} and \emph{Surveys in Geophysics}
are the favoured currently. I personally would be very interested in GMD. What
do you think? Also interesting would be the GJI, because the MT comparison was
published there, so it would be in the same place.
}

@@

A second topic we want to address is verification. New codes are generally
verified against analytical solutions. However, analytical and semi-analytical
solutions only exist for very simple models. There is no possibility to check
how good a computed response is, expect for comparing the result from different
modellers. If different modellers using different discretisation and
implementations of Maxwell's equations yield the same result it can give
confidence in the accuracy. Providing these two models and results from four
different codes should give a benchmark with which new codes can be compared
and validated.

@@

\clearpage  % TODO: Just for now while drafting, remove later!
\section{Codes}

The four codes under consideration are, in alphabetical order, \custem
\citep{GEO.19.Rochlitz}, \emg3d \citep{JOSS.19.Werthmuller}, \petgem
\citep{GJI.19.CastilloReyes}, and \simpeg \citep{CAG.15.Cockett}. All four
codes have their user-facing routines written in Python, while the underlying
heavy computation is mostly done in other languages (which is the normal case
in the scientific Python stack); all of them make heavy use of \texttt{NumPy}
\citep{CSE.11.VanDerWalt} and \texttt{SciPy} \citep{NM.20.Virtanen}. All are
“modern” open-source projects, meaning that they not only come with open-source
license, but they are also hosted in an online-hosted version-control system
with feedback and tracking possibilities (raising issues, filing pull
requests), have extensive online documentation including many examples, have
continuous integration to some degree, and also importantly are all easily
installable, without any user-side compilations.

In the following a quick rundown of the codes. It is, however, beyond the scope
of this article to go into every detail of the different modellers, and we
refer to their references and documentation.

\tabl[btp]{codecomparison}{Caption.}{
  \centering
  \small
\begin{tabular}{lcccc}
  \toprule
  %
  Code & \custem & \emg3d & \petgem & \simpeg  \\
  \midrule
  %
  Home & \href{https://custem.rtfd.io}{custem.rtfd.io}
       & \href{https://empymod.github.io}{empymod.github.io}
       & \href{http://petgem.bsc.es}{petgem.bsc.es}
       & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
  Installation & \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{pip}; \texttt{conda} \\
  License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
  Eq. system & ? & FIT & ? & ? \\
  Comp. Dom. & frequency & frequency & frequency & frequency \& time \\
  Mesh & FE & FD & FE & FD; OcTree; CylMesh \\
  BC & ? & PEC & ? & ? \\
  Methods & ? & Diffusion & ? & ? \\
  Solver & FEniCS$^\dagger$ & \emg3d & FEniCS$^\dagger$ &
           PARDISO$^\ddagger$; SciPy \\
  %
  \bottomrule
\end{tabular}}%
%
As is visible from Table~\ref{tbl:codecomparison}, we use two finite element
codes and two finite difference codes; the finite element codes both make use
of the FEniCS solver \citep{CSE.15.Alnaes}, whereas \simpeg can use either
solvers implemented in SciPy, or the PARDISO solver \citep{FGCS.04.Schenk};
\emg3d, on the other hand, is a solver on its own.

\imycom[DW]{
Each code should be briefly summarized by four points:\\
- Brief intro and main features\\
- Main selling point\\
- Planned features\\
- List (same list for all)\\
}

@@

@@

@@

\clearpage  % TODO: Just for now while drafting, remove later!
\section{Comparison}

@@

\clearpage  % TODO: Just for now while drafting, remove later!
\section{Discussion}

@@

\clearpage  % TODO: Just for now while drafting, remove later!
\section{Conclusions}

@@

\clearpage  % TODO: Just for now while drafting, remove later!
\section{Acknowledgment}

\imycom[DW]{Write here your fundings; and potentially also minor contributors etc.}

@@

\clearpage  % TODO: Just for now while drafting, remove later!
\section{Data}

@@

\clearpage  % TODO: Just for now while drafting, remove later!
% REFERENCES
\bibliographystyle{Refs}          % Modified SEG bibliography style.
\bibliography{Refs}
